Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes

### 2019-08-11 representation/representation.tex
change representation.tex
temp


temp
stable representation.tex


fix representation.tex

% * Preamble
\documentclass[xcolor=dvipsnames]{beamer}
\synctex=1
%\usepackage[UTF8,scheme=plain]{ctex}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{comment}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usetheme{Madrid}
\usecolortheme{seahorse}
\usecolortheme{rose}
\usefonttheme{serif}
\usefonttheme{structurebold}
\setbeamerfont{title}{shape=\itshape,family=\rmfamily}
\setbeamercolor{title}{fg=red!80!black,bg=red!20!white}
% * Top matter
\title[Stable CLT for Super OU]{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
\author[Z. Sun]{ 
  {\bf \Large Zhenyao Sun\inst{1}}
\\
{\scriptsize  Joint work with {\bf Yan-Xia Ren\inst{1}}, {\bf Renming Song\inst{2}} and {\bf Jianjie Zhao\inst{1} } }
}
\institute[PKU]{
\and
\inst{1}
	Peking University
\and
\inst{2}
	University of Illinois at Urbana-Champaign
}
\date[SHNU, July, 2019]{
	Shanghai Normal University,\\
	July, 2019}
\begin{document}

@@

\section{Model}
\subsection{Settings}
\begin{frame}{Model/Settings}
\begin{itemize}
\item
	$E$: a locally compact separable metric space.
\item
	$(\xi_t)_{t\geq 0}$: an $E$-valued Hunt process with semigroup $(P_t)_{t\geq 0}$. 
\item
	$\psi$: a function from $[0,\infty)$ to $\mathbb R$ given by 
\begin{equation} \label{eq: honogeneou branching mechanism}
    \psi(z)=
    - {\color{red} \alpha} z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \geq 0,
\end{equation}
	where ${\color{red}\alpha} > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with 
\[
	\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty.
\]
\item
  We call ${\color{red}\alpha}$ the {\color{red} branching rate}.
\end{itemize}
\end{frame}

\begin{frame}{Model/Settings}
\begin{itemize}
\item
	$\mathcal M(E)$: the space of all finite Borel measures on $E$ equipped with the weak topology.
\item
  $\left\langle f,\mu \right\rangle$: the integration of function $f$ and measure $\mu$ whenever it make senses.
\item
	Say a function $f$ on $\mathbb R_+\times E$ is \emph{locally bounded} if
\[
    \sup_{s\in [0,t],x\in E} |f(s,x)|
    <\infty,
    \quad t\in \mathbb R_+.
\]
\end{itemize}
\end{frame}

\subsection{Superprocesses}
\begin{frame}{Model/Superprocesses}
\begin{definition}[Superprocess]
	Say an $\mathcal M(E)$-valued Markov process $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu\in \mathcal M(E)}\}$ is a $(\xi,\psi)$-superprocess if for each bounded non-negative measurable function $f$ on $E$, we have
\begin{equation}
\label{eq: def of V_t}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(E),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{equation}
	V_tf(x) +  \int_0^t P_{t-s}(\psi \circ V_{s}f)(x)ds
	= P_tf(x),
    \quad x\in E, t\geq 0.
\end{equation}
\end{definition}
\end{frame}

\begin{frame}{Model/Superprocesses}
\begin{example}
	Let $\alpha >0$ and $\beta \in (0,1)$.
	Consider a Branching OU-process with
\begin{itemize}
\item
	{\color{red} $k$} initial particles;
\item
	killing rate  $2{\color{red}k}^\beta$;
\item
	offspring generating function
\[
	F_{\color{red}k}(x) =x +\frac{1}{2}(1-x)^{1+\beta} + \frac{-\alpha (1-x)}{2{\color{red}k}^\beta}.
\]
\end{itemize}
	Let $X^{({\color{red} k})}_t(A)$ be number of particles in a Borel set $A$ at time $t$. 
	Then,
\[
	\Big(\frac{1}{\color{red} k} X^{({\color{red} k})}_t(\cdot)\Big)_{t\geq 0}
	\xrightarrow[{\color{red}k}\to \infty]{w} (X_t)_{t\geq 0}
\]
where $(X_t)_{t\geq 0}$ is a super OU process with branching mechanism \[\psi(z) = -\alpha z + z^{1+\beta}.\]
\end{example}
\end{frame}

\section{Background}
\subsection{Motivation}

\begin{frame}{Background/Motivation}
  \begin{block}{Motivation}
    We are interested in the spatial laws of large numbers (LLNs) and central limit theorems (CLT) for superprocesses.
    More precisely, we want to find
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
    \[
      \frac{\langle f, X_t \rangle -G_t}{F_t}
    \]
\begin{itemize}
\item
converges in probability or in $L^p$ to a non-degenerate random variable (weak LLNs);
\item
converges almost surely to a non-degenerate random variable (strong LLNs);
\item
converges weakly to some non-degenerate random variable (CLTs).
\end{itemize}
  \end{block}
\end{frame}

\subsection{LLNs of superprocesses}
\begin{frame}{Background/LLNs of superprocesses}
\begin{itemize}
\item
{\color{red}Weak laws of large numbers} under different settings: Englander 2009, Englander and Winter 2006, Englander  and Turaev 2002.
\item
{\color{red}Strong law of large numbers} under different settings: Chen, Ren and Wang 2008, Wang 2010, Liu, Ren and Song 2013, Kouritzin and  Ren 2014, Chen, Ren, Song and Zhang 2015, Eckhoff, Kyprianou and Winkel 2015, Chen, Ren and Yang 2019.
\end{itemize}
\end{frame}

\begin{frame}{Background/LLNs of superprocesses}
\begin{example}[Chen, Ren and Yang 2019]
	Suppose that $X$ is a super OU process with branching mechanism $\psi(z)=-\alpha z+ z^{1+\beta}$ with $\alpha>0$ and $\beta \in (0,1)$. Then, for each $\mu \in \mathcal M(\mathbb R^d)$ and each continuous bounded non-negative function $f$ on $\mathbb R^d$, we have
\[
	e^{-\alpha t} \langle f, X_t\rangle \xrightarrow[t\to \infty]{\mathbb P_\mu \text{-a.s.}, L^1(\mathbb P_\mu)} H_\infty \langle f, \varphi\rangle,
\]
	where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\varphi$ is the invariant density of the OU process $\xi$.
\end{example}
\end{frame}

\subsection{CLTs for branching processes with 2rd moment conditions}
\begin{frame}{Background/CLTs for branching processes with 2rd moment conditions}
\begin{itemize}
\item
	For CLT of supercritical {\color{red} Galton-Watson processes}, see Heyde 1970, Heyde and Brown 1971, Heyde and Leslie 1971.
\item 
	For CLT of supercritical  {\color{red} multi-type Galton-Watson processes}, see Athreya 1969, Athreya 1969, Athreya 1971.
\item
	For CLT of some general supercritical {\color{red} branching Markov processes}, see Asmussen and Hering 1983.
\item
	For CLT of supercritical {\color{red} branching OU processes} with {\color{red} binary branching} mechanism, see Adamczak and Milos 2015.
\end{itemize}
\end{frame}

\begin{frame}{Background/CLTs for Superprocesses with 2rd moment conditions}
\begin{itemize}
\item
	For CLT of some supercritical {\color{red} superprocesses} with branching mechanisms satisfying a {\color{red} fourth moment condition}, see Milos 2018.
\item
	For CLT of supercritical {\color{red} super OU processes} with branching mechanisms satisfying only a {\color{red} second moment condition}, see Ren, Song and Zhang 2014.
\item
	For a series of CLT for a large class of general supercritical {\color{red} branching Markov processes} and {\color{red} superprocesses} with {\color{red} spatially dependent branching mechanisms} satisfying a {\color{red} second moment condition}, see Ren, Song and Zhang 2014, Ren, Song and Zhang 2015, Ren, Song and Zhang 2017.
\end{itemize}
\end{frame}

\subsection{Stable CLTs without the 2rd moment condition}
\begin{frame}{Background/Stable CLTs without the 2rd moment condition}
\begin{itemize}
\item
	For stable CLT for supercritical {\color{red} Galton-Watson process} whose {\color{red} offspring distribution
    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$}, see Heyde 1971.
\item
	For stable CLT for supercritical {\color{red} multi-type Galton-Watson process} and supercritical {\color{red} continuous time branching processes}, see Asmussen 1976.
\item
	Recently, some stable CLTs for supercritical {\color{red} branching OU processes} with offspring generating function
\[
    F(s)
    = ms -(m-1) +(m-1) (1-s)^{1+\beta},
    \quad |s|< 1
\]
	with $m>1$ and $\beta\in (0, 1)$ are established in Marks and Milos 2018.
\item
	Very recently, some stable fluctuation results of Biggins’ martingales in the context of {\color{red} branching random walks} are established in Iksanov, Kolesko and Meiners 2018.
\end{itemize}
\end{frame}

\section{Settings}
\begin{frame}{Settings}
\begin{itemize}
\item
	Let $E= \mathbb R^d$.
\item
	Let $(\xi_t)_{t\geq 0}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck (OU) process with generator
\[
	Lf(x)
	=\frac{1}{2} \sigma^2 \Delta f(x)-bx\cdot\nabla f(x),
	\quad x\in \mathbb R^d, f\in C^2(\mathbb R^d),
\]
	where $\sigma,b>0$.
\end{itemize}
\end{frame}

\begin{frame}{Settings/Assumption 1}

\begin{block}{Assumption 1. (Grey's condition)}
	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{block}
\begin{itemize}
\item
	It is known  that, under Assumption 1, 
	the \emph{extinction event} 
	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
\end{itemize}
\end{frame}

\begin{frame}{Settings/Assumption 2}
\begin{itemize}
\item
	Denote by $\Gamma$ the gamma function.
	For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
\end{itemize}
\begin{block}{Assumption 2.}
	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
\end{equation}
	for some $\delta \in (0,1-\beta)$.
\end{block}
\end{frame}

\begin{frame}{Settings/Assumption 2}
\begin{itemize}
\item
	Assumption 2 says that 
 there exist constants $\eta>0$ and $\beta > 0$ 
    such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
\item
    In particular, if \[\pi(dy)=\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy,\] then the branching mechanism takes the form: \[\psi(z)=-\alpha z + \rho z^2 + \eta z^{1+\beta},\quad z\geq 0.\]
\end{itemize}
\end{frame}

\section{Preliminary}
\begin{frame}{Preliminary/Invariant measure of OU semigroup}
\begin{itemize}
\item
  Recall that $(P_t)_{t\geq 0}$ is the transition semigroup of the OU process $\xi$.
\item
  $(P_t)_{t\geq 0}$ has the invariant density
\begin{equation}
    \varphi(x)dx
    :=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb R^d.
\end{equation}
\item
    Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x).
\end{equation}
\end{itemize}
\end{frame}

\begin{frame}{Preliminary/Hermite polynomials}
\begin{itemize}
\item
    For each multi-index $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write 
\begin{equation}
	|p|:=\sum_{k=1}^d p_k;
	\quad p!:= \prod_{k= 1}^d p_k!;
	\quad \frac{\partial^p} {\partial x^p}:= \prod_{k = 1}^d\frac{\partial^{p_k}}{\partial x_k^{p_k}}.
\end{equation}
\item
    The \emph{Hermite polynomials} are given by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{p}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    p \in \mathbb{Z}_+^{d}.
\end{equation}
\end{itemize}
\end{frame}

\begin{frame}{Preliminary/Spectrum of OU semigroup}

\begin{lemma}[Metafune, Pallara and Priola 2002]
	$(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\[
    \mathcal{A}_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\]
    where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
	Moreover, $\{\phi_p:p\in \mathbb Z_+^d\}$ forms a complete orthonormal basis for $L^2(\varphi)$.
\end{lemma}
\end{frame}

\begin{frame}{Preliminary/Order of a testing function}
\begin{itemize}
\item
    For each function $f\in L^2(\varphi)$, denote by
\begin{equation}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
\end{equation}
    the order of the function $f$. 
\item
	We say a function $f\in \mathcal B(\mathbb R^d, \mathbb R)$ is of polynomial growth if there exists constants $C,n>0$ such that 
\[
	|f(x)|\leq C(1+|x|)^n,
	\quad \forall x\in \mathbb R^d.
\]
\item
    $\mathcal P$: the collection of all functions of polynomial growth.
\end{itemize}
\end{frame}

\section{Results}
\begin{frame}{Results/Phase transition}
\begin{itemize}
\item
  Recall that $\alpha$ is the branching rate.
\item
	It turns out that the CLTs of $\left\langle f,X_t \right\rangle$ are different in three different regimes
    depending on the sign of $\alpha-\frac{\kappa_f b (1+\beta)}{\beta}$:
\begin{itemize}
\item
  small branching rate regime: $\alpha < \frac{\kappa_f b (1+\beta)}{\beta}$;
\item
  critical branching rate regime: $\alpha = \frac{\kappa_f b (1+\beta)}{\beta}$;
\item
  large branching rate regime: $\alpha > \frac{\kappa_f b (1+\beta)}{\beta}$.
\end{itemize}
\end{itemize}
\end{frame}
\begin{frame}{Results/Small branching rate regime/ CLT}
\begin{theorem}[Ren, Song, S. and Zhao 2019+]
    Let $f\in \mathcal{P}\setminus\{0\}$ satisfy $\alpha\beta<\kappa_f b(1+\beta)$.
    Let $\mu\in \mathcal M(\mathbb R^d)$ have compact support. Then under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \|X_t\|^{-\frac{1}{1+\beta}} \langle f,X_t\rangle\xrightarrow[t\rightarrow \infty]{d} \zeta.
\]
    Here, $\zeta$ is a $(1+\beta)$-stable random variable with characteristic function $\theta \mapsto \exp( m[\theta f])$ with 
    \begin{equation}
      m[\theta f]
      :=\eta \int_0^{\infty} e^{-\alpha s} ~ds\int_{\mathbb R^d} \big(-i \theta P_s^\alpha f(x)\big)^{1+\beta} \varphi(x)~dx.
    \end{equation}
\end{theorem}
\end{frame}

>>>>

% * Preamble
\documentclass[xcolor=dvipsnames]{beamer}
\synctex=1
%\usepackage[UTF8,scheme=plain]{ctex}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{comment}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usetheme{Madrid}
\usecolortheme{seahorse}
\usecolortheme{rose}
\usefonttheme{serif}
\usefonttheme{structurebold}
\setbeamerfont{title}{shape=\itshape,family=\rmfamily}
\setbeamercolor{title}{fg=red!80!black,bg=red!20!white}
% * Top matter
\title[Stable CLT for superprocesses]{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}
\author[Zhenyao Sun]{ 
  {\bf \Large Zhenyao Sun  }
}
\institute[WHU]{Wuhan University\\
  Joint work with {\bf Yan-Xia Ren}, {\bf Renming Song} and {\bf Jianjie Zhao}}
\date[]{
	Peking University,
 \\ August, 2019}
\begin{document}

@@

% * Presentation
% ** Model
\section{Model}
% *** Settints
\subsection{Settings}
\begin{frame}{Model/Settings}
\begin{itemize}
\item
	$E$: a locally compact separable metric space.
\item
	$(\xi_t)_{t\geq 0}$: an $E$-valued Hunt process with semigroup $(P_t)_{t\geq 0}$. 
\item
	$\psi$: a function from $[0,\infty)$ to $\mathbb R$ given by

  \[\psi(z)=
  - {\color{red} \alpha} z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) {\color{blue}\pi(dy)},
  \quad  z \geq 0,
  \]

	where ${\color{red}\alpha > 0}$, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with

\[
	\int_{(0,\infty)}(y\wedge y^2) {\color{blue}\pi(dy)}
  < \infty.
\]

\item
  We call ${\color{red}\alpha}$ the {\color{red} branching rate}; ${\color{blue} \pi(dy)}$ the {\color{blue} L\'evy measure}.
\end{itemize}
\end{frame}

\begin{frame}{Model/Settings}
\begin{itemize}
\item
	$\mathcal M(E)$: the space of all finite Borel measures on $E$ equipped with the weak topology.
\item
  $\mu(f)$ and $\langle f, \mu\rangle$: the integration of function $f$ and measure $\mu$ whenever it make senses.
\item
	Say a function $f$ on $\mathbb R_+\times E$ is locally bounded if
\[
    \sup_{s\in [0,t],x\in E} |f(s,x)|
    <\infty,
    \quad t\in \mathbb R_+.
\]
\end{itemize}
\end{frame}

% *** Superprocesses
\subsection{Superprocesses}
\begin{frame}{Model/Superprocesses}
\begin{definition}[Superprocess]
	Say an $\mathcal M(E)$-valued Markov process $\{(X_t)_{t\geq 0}; (\mathbb P_\mu)_{\mu\in \mathcal M(E)}\}$ is a $(\xi,\psi)$-superprocess if for each bounded non-negative measurable function $f$ on $E$, we have
\begin{equation}
\label{eq: def of V_t}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(E),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{equation}
	V_tf(x) +  \int_0^t P_{t-s}(\psi \circ V_{s}f)(x)ds
	= P_tf(x),
    \quad x\in E, t\geq 0.
\end{equation}
\end{definition}
\end{frame}

\begin{frame}{Model/Superprocesses}
\begin{example}
	Let $\alpha >0$ and ${\color{red} \beta} \in (0,1)$.
	Consider a branching Ornstein-Uhlenbeck(OU) process with
\begin{itemize}
\item
	{\color{blue} $k$} initial particles at the origin;
\item
	killing rate  $2{\color{blue} k}^{\color{red}\beta}$;
\item
	offspring generating function
\(
	F_{\color{blue} k}(x) =x +\frac{1}{2}(1-x)^{1+{\color{red}\beta}} + \frac{-\alpha (1-x)}{2{\color{blue} k}^{\color{red}\beta}}.
\)
\end{itemize}
	Let $X^{({\color{red} k})}_t(A)$ be number of particles in a Borel set $A$ at time $t$. 
	Then,
\[
	\Big(\frac{1}{\color{blue} k} X^{({\color{blue} k})}_t(\cdot)\Big)_{t\geq 0}
	\xrightarrow[{\color{blue} k}\to \infty]{d} (X_t)_{t\geq 0}
\]
where $(X_t)_{t\geq 0}$ is a super-OU process with branching mechanism \[\psi(z) = -\alpha z + z^{1+{\color{red}\beta}}.\]
\end{example}
\end{frame}

% ** Background
\section{Background}
% *** Motivation
\subsection{Motivation}
\begin{frame}{Background/Motivation}
  \begin{block}{Motivation}
    We are interested in the spatial laws of large numbers (LLNs) and central limit theorems (CLT) for superprocesses.
    More precisely, for a testing function $f$, we want to find
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
    \[  
      \frac{\langle f, X_t \rangle -G_t}{F_t}
    \]

    \begin{itemize}
    \item
      converges in probability or in $L^p$ to a non-degenerate random variable (weak LLNs);
    \item
      converges almost surely to a non-degenerate random variable (strong LLNs);
    \item
      converges weakly to some non-degenerate random variable (CLTs).
    \end{itemize}
  \end{block}
\end{frame}
% *** LLNs of superprocesses
\subsection{LLNs of superprocesses}
\begin{frame}{Background/LLNs of superprocesses}
\begin{itemize}
\item
  {\color{red}Weak LLNs of supercritical superprocesses} under different settings:

  \mbox{ $\circ$ J. Engl\"{a}nder and D. Turaev 2002 (AP);}
  \mbox{ $\circ$ J. Engl\"{a}nder and A. Winter 2006 (AIHPPS);}
  \mbox{ $\circ$ J. Engl\"{a}nder 2009 (AIHPPS);} 
\end{itemize}
\let\thefootnote\relax\footnotetext{
  \mbox{(AP) = Ann. Probab.;} 
  \mbox{(AIHPPS) = Ann. Inst. H. Poincar\'e Probab. Statist.}
}
\end{frame}

\begin{frame}{Background/LLNs of superprocesses}
\begin{itemize}
\item
  {\color{red} Strong LLNs of supercritical superprocesses} under different settings:

  \mbox{ $\circ$ Z.-Q. Chen, Y.-X. Ren and H. Wang 2008 (JFA);} 
  \mbox{ $\circ$ L. Wang 2010 (JTP);} 
  \mbox{ $\circ$ R.-L. Liu, Y.-X. Ren and R. Song 2013 (AAM);} 
  \mbox{ $\circ$ M. A. Kouritzin and Y.-X. Ren 2014 (SPA);} 
  \mbox{ $\circ$ Z.-Q. Chen, Y.-X. Ren, R. Song and R. Zhang 2015 (FMC);} 
  \mbox{ $\circ$ M. Eckhoff, A. E. Kyprianou and M. Winkel 2015 (AP);} 
  \mbox{ $\circ$ Z.-Q. Chen, Y.-X. Ren and T. Yang 2019 (AAM).}
\end{itemize}
\let\thefootnote\relax\footnotetext{
  \mbox{(JFA) = J. Funct. Anal.;}
  \mbox{(JTP) = J. Theoret. Probab.;}
  \mbox{(AAM) = Acta Appl. Math.;}
  \mbox{(SPA) = Stochastic Process. Appl.;}
  \mbox{(FMC) = Front. Math. China.}
}
\end{frame}

\begin{frame}{Background/LLNs of superprocesses}
\begin{example}
	Suppose that $X$ is a super OU process with branching mechanism $\psi(z)=-\alpha z+ z^{1+\beta}$ with $\alpha>0$ and $\beta \in (0,1)$. Then, for each $\mu \in \mathcal M(\mathbb R^d)$ and each continuous bounded non-negative function $f$ on $\mathbb R^d$, we have
\[
	e^{-\alpha t} X_t(f) \xrightarrow[t\to \infty]{\mathbb P_\mu \text{-a.s.}, L^1(\mathbb P_\mu)} H_\infty \int f(x) \varphi(x) dx,
\]
	where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\|X_t\|$ and $\varphi$ is the invariant probability density of the OU process $\xi$.
\end{example}
\end{frame}

\subsection{CLTs for branching processes with the 2rd moment condition}
\begin{frame}{Background/CLTs for branching processes with 2rd moment conditions}
\begin{itemize}
\item
	{\color{red} CLT of supercritical Galton-Watson(GW) processes} with finite offspring variance:

  \mbox{ $\circ$ C. C. Heyde 1970 (JAP);}
  \mbox{ $\circ$ C. C. Heyde and B. M. Brown 1971 (ZWVG);}
  \mbox{ $\circ$ C. C. Heyde and J. R. Leslie 1971 (BAMS).}
\item 
	{\color{red} CLT of supercritical multi-type GW processes} with a 2rd moment condition:

  \mbox{ $\circ$ K. B. Athreya 1969a (ZWVG);}
  \mbox{ $\circ$ K. B. Athreya 1969b (ZWVG);} 
  \mbox{ $\circ$ K. B. Athreya 1971 (ZWVG).}
\end{itemize}
\let\thefootnote\relax\footnotetext{
  \mbox{(JAP) = J. Appl. Probability;}
  \mbox{(ZWVG) = Z. Wahrsch. Verw. Gebiete;}
  \mbox{(BAMS) = Bull. Austral. Math. Soc.}
}
\end{frame}

\begin{frame}{Background/CLTs for branching processes with 2rd moment conditions}
\begin{itemize} 
\item
  {\color{red} CLT of supercritical branching OU processes} with binary branching:

  \mbox{ $\circ$ R. Adamczak and P. Mi{\l}o{\'s} 2015 (EJP).}
\item
	{\color{red} CLT of some general supercritical branching Markov processes} with a 2rd moment condition:

  \mbox{ $\circ$ S. Asmussen and H. Hering 1983 (book);}
  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2014 (JFA);}
  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2017 (AP).}
\end{itemize}
\let\thefootnote\relax\footnotetext{
  \mbox{(EJP) = Electron. J. Probab.}
}
\end{frame}

\begin{frame}{Background/CLTs for Superprocesses with 2rd moment conditions}
\begin{itemize}
\item
	{\color{red} CLT of supercritical superprocesses} with a fourth moment condition:

  \mbox{ $\circ$ P. Mi{\l}o\'{s} 2018 (JTP).}
\item
	{\color{red} CLT of supercritical super OU processes} with a 2rd moment condition:

  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2014 (AAM).}
\item
	{\color{red} CLT for a large class of general supercritical superprocesses} with a 2rd moment condition:

  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2015 (SPA);}
  \mbox{ $\circ$ Y.-X. Ren, R. Song and R. Zhang 2017 (AAM).}
\end{itemize}
\end{frame}

\subsection{Stable CLTs without the 2rd moment condition}
\begin{frame}{Background/Stable CLTs without the 2rd moment condition}
\begin{itemize}
\item
	{\color{red} Stable CLT for supercritical GW processes:}

  \mbox{ $\circ$ C. C. Heyde 1971 (JAP).}
\item
	{\color{red} Stable CLT for supercritical multi-type GW process:}

  \mbox{ $\circ$ S. Asmussen 1976 (AP).}
\item
	{\color{red} Stable CLTs for supercritical branching OU processes} with offspring generating function

\( \displaystyle
    \qquad F(s)
    = ms -(m-1) +(m-1) (1-s)^{1+\beta},
    \quad |s|< 1
\)

	where $m>1$ and $\beta\in (0, 1)$:

  \mbox{ $\circ$ R. Marks and P. Mi{\l}o{\'s} 2018 (arXiv).}
\item
	{\color{red} Stable fluctuation results of Biggins’ martingales of branching random walks:}

  \mbox{ $\circ$ A. Iksanov, K. Kolesko and M. Meiners 2018 (SPA).}
\end{itemize}
\end{frame}

\section{Settings}
\begin{frame}{Settings/Assumption 1}
\begin{itemize}
\item
	$E:= \mathbb R^d$.
\item
  $\xi = (\xi_t)_{t\geq 0}$, an $\mathbb R^d$-valued OU process with generator

  \( \displaystyle \qquad
	Lf(x)
	=\frac{1}{2} \sigma^2 \Delta f(x)-bx\cdot\nabla f(x),
	\quad x\in \mathbb R^d, f\in C^2(\mathbb R^d),
  \)

	where $\sigma,b>0$.
\end{itemize}
\begin{block}{Assumption 1. (Grey's condition)}
	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  
  \centerline{ \( \displaystyle
    \int_{z'}^\infty \psi(z)^{-1}dz 
    < \infty.
    \)}
\end{block}
\begin{itemize}
\item
	Under Assumption 1, write $D := \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$, then

  \centerline{ \( \displaystyle
    \mathbb P_\mu(D)
    > 0, 
    \quad \mu \in \mathcal M(\mathbb R^d).
  \)}
\end{itemize}
\end{frame}

\begin{frame}{Settings/Assumption 2}
\begin{itemize}
\item
	$\Gamma$: the gamma function.
\item
	$|\mu|$: the total variation measure of some measure $\mu$.
\item
  Recall that $\pi$ is the L\'evy measure of the branching mechanism $\psi$.
\end{itemize}
\begin{block}{Assumption 2.}
	There exist (unique) constants ${\color{red}\eta} > 0$ and ${\color{red}\beta} \in (0,1)$ such that for some $\delta \in (0, 1- {\color{red}\beta})$ it holds that
  \centerline{ \( \displaystyle	
    \int_{(1,\infty)}y^{1+{\color{red}\beta} +\delta}~\Big|\pi(dy)-\frac{{\color{red}\eta}~dy}{\Gamma(-1-{\color{red}\beta})y^{2+{\color{red}\beta}}}\Big| 
    <\infty.
    \)}
\end{block}
\begin{itemize}
\item
    In particular, if 
    \( \displaystyle
    \pi(dy)
    =\frac{{\color{red}\eta} dy}{ \Gamma(-1-{\color{red}\beta})y^{2+{\color{red}\beta}}},
    \) 
    then the branching mechanism takes the form: 
    \( 
    \psi(z)
    = -\alpha z + \rho z^2 + {\color{red}\eta} z^{1+{\color{red}\beta}}
    ,\quad z\geq 0.
    \)
\end{itemize}
\end{frame}

\section{Preliminary}
\begin{frame}{Preliminary/Hermite polynomials}
\begin{itemize}
\item
  Recall that $(P_t)_{t\geq 0}$ is the transition semigroup of the OU process $\xi$.
\item
  $(P_t)_{t\geq 0}$ has the invariant probability

  \centerline{ \( \displaystyle	
    \varphi(x)~dx
    := \Big(\frac{b}{\pi \sigma^2} \Big)^{\frac{d}{2}} e^{-\frac{b}{\sigma^2}|x|^2}~dx,
    \quad x\in \mathbb R^d.
    \)}
\item
  $L^2(\varphi)$: the Hilbert space with inner product

  \centerline{ \( \displaystyle    
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x)~dx.
    \)}
\item
    For each multi-index $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write

    \centerline{ \( \displaystyle	
      |p|:=\sum_{k=1}^d p_k;
      \quad p!:= \prod_{k= 1}^d p_k!;
      \quad \frac{\partial^p} {\partial x^p}:= \prod_{k = 1}^d\frac{\partial^{p_k}}{\partial x_k^{p_k}}.
      \)}
\item
    Define the \emph{Hermite polynomials} by

    \centerline{ \( \displaystyle
      H_p(x)
      :=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{p}}{\partial x^p} e^{-|x|^2} ,
      \quad x\in \mathbb R^d,
      p \in \mathbb{Z}_+^{d}.
      \)}
\end{itemize}
\end{frame}

\begin{frame}{Preliminary/Spectrum of OU semigroup}
\begin{block}{Fact}
	$(P_t)_{t\geq 0}$ is a strongly continuous semigroup on $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
  For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then

  \[
    \mathcal{A}_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
  \]

    where

    \[
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
    \]

    Moreover, $\{\phi_p:p\in \mathbb Z_+^d\}$ forms a complete orthonormal basis for $L^2(\varphi)$.
\end{block}
\end{frame}
